Price of Anarchy for Mean Field Games

### 2018-07-20 PoA.tex
minor edits again

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\label{eq:eta_bar_MKV}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MKV}
\end{equation}
And thus,
\begin{equation}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\label{eq:x_bar_MKV}
\end{equation}
\begin{equation}
v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\label{eq:v_t_MKV}
\end{equation}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

@@

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. For every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	Again, by the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{r\to \infty,MFG})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
	\end{equation*}

	%---------------------------
	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	 $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV,r} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA^r = 1$. Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.

@@

% proposition b_2
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$. Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.

	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\begin{split}
	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
	\end{split}
	\end{equation*}

@@

		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u . \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u . \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }

@@

		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 . e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\

@@

		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]. e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt

@@

%proposition 5
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
	then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

>>>>

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\label{eq:eta_bar_MKV}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MKV}
\end{equation}
And thus,
\begin{equation}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\end{equation}
\begin{equation}
v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\label{eq:v_t_MKV}
\end{equation}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. For every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\left\vert u_t^{r} \right\vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	Again, by the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	 $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV,r} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA^r = 1$. Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{MFG,0,b_2}$, which is bounded over $[0,T]$. Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.

	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\begin{split}
	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{MFG,0,b_2})^2 dt,\\
	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
	\end{split}
	\end{equation*}

@@

		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }

@@

		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 \cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\

@@

		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
	then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.
